Solving the maximum independant set problem with Tropical tensor networks

### 2021-05-18 paper/paper.tex
update

\newtheorem{theorem}{\textit{Theorem}}
\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}

@@

\section{Computing degeneracy}
\section{Utilizing the sparsity}
Tensor network compression is an important tool to utilize sparsity.
\subsection{The equivalence between branching and compression}
We contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
The maximum independant set size in this region with boundary configuration $\sigma \in \{0,1\}\otimes |C|$ is $A_{\sigma}$.
We say an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
\begin{align}
(\sigma_a \land \sigma_b = \sigma_a) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}
\end{align}
where $\land$ is a bitwise and operations.
The first term means that whenever a bit in $\sigma_a$ has boolean value $1$, the corresponding bit in $\sigma_b$ is also $1$.
While the second term means the maximum independant set size with boundary configuration fixed to $\sigma_a$ is not less than that fixed to $\sigma_b$.
The word ``better'' means the best solution with boundary configuration $\sigma_a$ is never worse than that with $\sigma_b$.
When Eq. \ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.
\section{Vertifying a widget}

\section{}

>>>>

\newtheorem{theorem}{\textit{Rule}}
\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}

@@

\section{Computing degeneracy}
\section{Utilizing the sparsity}
Tensor network compression is an important tool to utilize sparsity.

We contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
The maximum independant set size in this region with boundary configuration $\sigma \in \{0,1\}\otimes |C|$ is $A_{\sigma}$.
We say an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
\begin{align}
(\sigma_a \land \sigma_b = \sigma_a) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}
\end{align}
where $\land$ is a bitwise and operations.
The first term means that whenever a bit in $\sigma_a$ has boolean value $1$, the corresponding bit in $\sigma_b$ is also $1$.
While the second term means the maximum independant set size with boundary configuration fixed to $\sigma_a$ is not less than that fixed to $\sigma_b$.
The word ``better'' means the best solution with boundary configuration $\sigma_a$ is never worse than that with $\sigma_b$.
When Eq. \ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.

\subsection{The equivalence between branching and compression}
We are going the verify the Lemmas used in branching algorithm in book~\cite{Fomin2013}.
\begin{theorem} % basic
  If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
On the other hand, if $I$ is a maximum (and thus maximal) independent set,
and thus if $v$ is not in $I$ then at least one of its neighbors is in $I$.
\end{theorem}
\begin{theorem} % 2.6
Let $G=(V,E)$ be a graph, let $v$ and $w$ be adjacent vertices of $G$ such that $N[v] \subseteq N[w]$. Then
\begin{equation}
\alpha(G)=\alpha(G\backslash w).
\end{equation}
\end{theorem}

\begin{theorem} % 2.7
  Let $G = (V, E)$ be a graph and let $v$ be a vertex of $G$. If no maximum
independent set of $G$ contains $v$ then every maximum independent set of $G$ contains
at least two vertices of $N(v)$.
\end{theorem}

\begin{theorem} % 2.8
Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
\begin{equation}
\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
\end{equation}
\end{theorem}

\begin{theorem} % 2.9
Let $G = (V, E)$ be a graph and $v$ be a vertex of $G$ such that $N[v]$ is a
clique. Then
\begin{equation}
\alpha(G) = 1 + \alpha(G \backslash N[v]).
\end{equation}
\end{theorem}

\begin{theorem}  %2.10
Let $G$ be a graph, let $S$ be a separator of $G$ and let $I(S)$ be the set of
all subsets of $S$ being an independent set of $G$. Then
\begin{equation}
\alpha(G) = \max_{A\in I(S)} |A| + \alpha(G \backslash (S \cup N[A])).
\end{equation}
\end{theorem}

\begin{theorem}  %2.11
Let $G = (V, E)$ be a disconnected graph and $C \subseteq V$ a connected com-
ponent of $G$. Then
\begin{equation}
\alpha(G) = \alpha(G[C]) + \alpha(G \backslash C)).
\end{equation}
\end{theorem}

\begin{align}
if |V| = 0 then
return 0
if \exists v \in V with d(v) \leq 1 then
return 1 + mis2(G \backslash N[v])
if \exists v \in V with d(v) = 2 then
(let u 1 and u 2 be the neighbors of v)
if {u 1 , u 2 } \in E then
return 1 + mis2(G \backslash N[v])
if {u 1 , u 2 } \in
/ E then
if |N 2 (v)| = 1 then
(let N 2 (v) = {w})
return max(2 + mis2(G \backslash (N 2 [v] \cup N[w])), 2 + mis2(G \backslash N 2 [v]))
if |N 2 (v)| > 1 then
return max(mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
if \exists v \in V with d(v) = 3 then
(let u 1 u 2 and u 3 be the neighbors of v)
if G[N(v)] has no edge then
if v has a mirror then
return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup {v}))
if v has no mirror then
return max(1 + mis2(G \backslash N[v]), 2 + mis2(G \backslash N[{u 1 , u 2 }]), 2 + mis2(G \backslash
(N[{u_1 , u_3 }] \cup \{u_2\})), 2 + mis2(G \backslash (N[{u_2 , u_3 }] \cup \{1\})))
if G[N(v)] has one or two edges then
return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
if G[N(v)] has three edges then
return 1 + mis2(G \backslash N[v])
if \Delta (G) \geq 6 then
choose a vertex v of maximum degree in G
return max(1 + mis2(G \backslash N[v]), mis2(G \backslash v))
if G is disconnected then
(let C \subseteq V be a component of G)
return mis2(G[C]) + mis2(G \backslash C)
if G is 4 or 5-regular then
choose any vertex v of G
return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup \{v\}))
if \Delta (G) = 5 and \delta (G) = 4 then
choose adjacent vertices v and w with d(v) = 5 and d(w) = 4 in G
return
\max(1 + mis2(G \backslash N[v]), 1 + mis2(G \backslash (\{v\} \cup M(v) \cup N[w])), mis2(G \backslash (M(v) \cup \{v, w\})))
\end{align}
